---
title: "p8105_hw2_bl2898"
author: "Boqian Li"
date: "10/18/2021"
output: html_document
---

```{r}
library(tidyverse)
```

### Problem 1
```{r}
library(p8105.datasets)
data("instacart")
```
## How many aisles are there?
```{r}
instacart %>% 
    count(aisle) %>% 
    nrow() ## there are 134 aisles.
```
## Which aisles are the most items ordered from?
```{r}
instacart %>% 
    count(aisle, sort = TRUE) %>% 
    print() ## fresh vegetable has the most item.
```
## Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart %>% 
    count(aisle, sort = TRUE) %>% 
    filter(n >= 10000) %>% 
    ggplot(aes(x = n, y = aisle)) + geom_point() + 
    labs(
    title = "Number of items ordered in each aisle",
    x = "Aisle",
    y = "Number of items ordered"
  )
```
## Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
baking_ingredient <- 
    instacart %>% 
    filter(aisle == "baking ingredients") %>% 
    count(product_name,aisle,sort = TRUE) %>% 
    slice(1:3)

dog_food_care <- 
    instacart %>% 
    filter(aisle == "dog food care") %>% 
    count(product_name,aisle,sort = TRUE) %>% 
    slice(1:3)

package_veg <- 
    instacart %>% 
    filter(aisle == "packaged vegetables fruits") %>% 
    count(product_name,aisle,sort = TRUE) %>% 
    slice(1:3)
    
table_popular <- cbind(
    baking_ingredient,
    dog_food_care,
    package_veg
)

print(table_popular)
```
## Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}

instacart %>% 
    filter(product_name == "Coffee Ice Cream") %>% 
    select(product_name,order_hour_of_day,order_dow) %>% 
    summarise(mean_hour = mean(order_hour_of_day)) %>%
    group_by(product_name,order_dow)

instacart %>% 
    filter(product_name == "Pink Lady Apples") %>% 
    select(product_name, order_hour_of_day, order_dow) %>% 
    summarise(mean_hour = mean(order_hour_of_day)) %>%
    group_by(product_name,order_dow)

```

### Problem 2

## clean data
```{r}
data("brfss_smart2010") 
BRFSS = 
  brfss_smart2010 %>%
  janitor::clean_names() %>%
  filter(topic == "Overall Health") %>%
  mutate(response = factor(response, c("Poor","Fair","Good","Very good","Excellent")))
BRFSS
```
## In 2002, which states were observed at 7 or more locations? 
```{r}
BRFSS %>% 
    select(year, locationabbr, locationdesc) %>% 
    filter(year == "2002") %>% 
    group_by(year,locationabbr) %>% 
    summarise(num_location = n_distinct(locationdesc)) %>% 
    filter(num_location >= 7) %>% 
    select(locationabbr)
```
## What about in 2010?
```{r}
BRFSS %>% 
    select(year, locationabbr, locationdesc) %>% 
    filter(year == "2010") %>% 
    group_by(year,locationabbr) %>% 
    summarise(num_location = n_distinct(locationdesc)) %>% 
    filter(num_location >= 7) %>% 
    select(locationabbr)
```
## Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).
```{r}
BRFSS %>% 
    filter(response == "Excellent") %>% 
    drop_na(data_value) %>%
    select(year, locationabbr, locationdesc, data_value) %>% 
    group_by(year, locationabbr) %>% 
    summarise(average_value = mean(data_value)) %>% 
    ggplot(aes(x = year, y = average_value, color = locationabbr)) +
    geom_line()+
    labs(
        x = "Year",
        y = "average of data_value",
        title = "average of data_value"
    ) 
```
## Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}
BRFSS %>% 
    filter(response %in% c("Poor","Fair","Good","Very good","Excellent"), 
           year %in% c(2006, 2010), locationabbr == "NY") %>%
    ggplot(aes(x = data_value, fill = response)) + 
    geom_density(alpha = .5, adjust = 0.8) +
    facet_grid(. ~ year) +
    labs(
        title = "Distribution plot of data value",
        x = "Data value",
        y = "Density"
    )
```
### Problem 3
```{r}
accel_data <- read_csv("accel_data.csv")
```
## Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
```{r}
accel_data %>% 
    janitor::clean_names() %>% 
    mutate(day = factor(day,c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")))
## There are 35 rows and 1443 columns. For all variable, day variable is character and others are numeric.
```
## Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?
```{r}
accel_data %>%
    pivot_longer(
        activity.1:activity.1440
    ) %>% 
    group_by(day_id) %>% 
    summarise(total_activity = sum(value))
  ## there are three days that the total activiy are extremly low compare to other days.
```
## Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.
```{r}
accel_data %>%
  pivot_longer(
    activity.1:activity.1440,
    names_to = "minute",
    names_prefix = "activity",
    values_to = "value"
  ) %>%
  group_by(day_id) %>%
  ggplot(
    aes(x = minute, y = value, color = day)
  ) +
  geom_line() +
  labs(
    title = "Activity plot",
    x = "Minutes",
    y = "Activity"
  ) 

```


